\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumerate}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large Advanced Test 1}
  \\ \vspace{1em}
  \textbf{\large Stellenbosch Camp 2021}
  \\ \vspace{1em}
  \textbf{\large Time: $2\frac{1}{2}$ hours}
\end{center}

\vspace{24pt}

\begin{enumerate}[1.]

\item % Ireland 2014
How many ways are there to choose $24$ black squares from a standard chess board (with $32$ black and $32$ white squares alternating) such that exactly three squares are chosen in each row and in each column?


\item % 2012 Estonian Winter Open Contest in Mathematics, Junior division
Triangle $ABC$ has $AC=BC$ and is right-angled at $C$. points $K$, $L$ are chosen on side $AC$ and points $M$, $N$ on side $BC$. It turns out that $K$ and $L$ divide the side $AC$ into three equal parts. Similarly, $M$ and $N$ divide $BC$ into three equal parts. Prove that there exists precisely one point $P$ interior to $ABC$ such that $\angle KPL = \angle MPN = 45^{\circ}$.


\item % 105 Algebra Problems, Andreescu
If $a$, $b$, and $c$ are real numbers in $(0,4)$, prove that at least one of the numbers
\[ \frac{1}{a} +\frac{1}{4-b}, \quad \frac{1}{b} +\frac{1}{4-c}, \quad\text{and}\quad \frac{1}{c} +\frac{1}{4-a} \]
is greater than or equal to $1$.


\item % Number Theory Marathon Question 12 from Liam's collection of resources
Find all natural numbers $n$ such that every prime divisor of $n^6 - 1$ is also a prime divisor of $(n^2 - 1)(n^3 - 1)$. 


\item % 1999 Estonian IMO TST Q4
A $30 \times 30$ grid is covered by $1 \times 2$ non-overlapping rectangular pieces (placed horizontally or vertically) until no more rectangular pieces can be added. (The pieces are placed in arbitrary locations on the grid, but each piece covers two of the cells in the grid.) Prove that when no more rectangles can be added, at least $300$ small rectangles have been placed.

\end{enumerate}


\vfill
\begin{itemize}
	\item Submit your solutions at \href{https://forms.gle/T9HNgZgj8EhypBnR6}{https://forms.gle/T9HNgZgj8EhypBnR6}
	\item Submit each question in a single separate PDF file (with multiple pages if necessary).
	\item If you take photographs of your work, use a document scanner such as Office Lens to convert to PDF.
	\item If you have multiple PDF files for a question, combine them using software such as PDFsam.
\end{itemize}

\vfill
% ASCII art
\centering
\begin{BVerbatim}
              ,-.
             /  (  '
     *  _.--'!   '--._
      ,'              ''.
'    |!                   \
   _.'  O      ___       ! \
  (_.-^, __..-'  ''''--.   )
      /,'        '    _.' /
   '         *    .-''    |
                 (..--^.  ' 
                  mrf  | /
                       '
\end{BVerbatim}

\end{document}
