\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large Advanced Test 4}
  \\ \vspace{1em}
  \textbf{\large Stellenbosch Camp 2021}
  \\ \vspace{1em}
  \textbf{\large Time: $2\frac{1}{2}$ hours}
\end{center}

\bigskip

\begin{enumerate}[itemsep=\fill]

\item % Andrew
Let $p$ be an odd prime. Prove that
\[
	\sum_{k=1}^{p-1} (p-k)!k! \equiv \frac{p-1}{2} \pmod{p}
\]


\item %
Phil the physicist tries to come up with some equations describing the behaviour of a bucket of salt water as it is diluted by adding pure water. He uses an $m$ kilogram bucket initially containing $s$ kgs of salt and $w$ kgs of water, before $x$ kgs of extra water is added. He uses $k$ as a positive proportionality constant. Phil realises that the following two expressions are important in his study. 
$$\frac{ms+mw}{\frac{kms}{ms+mw}+1} + mx$$
$$\frac{ms+mw+mx}{\frac{kms}{ms+mw+mx}+1}$$
Help Phil by determining which one of these expressions is always bigger than or equal to the other.

\item % Wherever Andrew got it from
Let $ABCD$ be a convex quadrilateral with an inscribed circle whose centre is $O$. Let $W$ and $X$ be the feet of the perpendiculars from $A$ onto $OB$ and $OD$ respectively. Let $Y$ and $Z$ be the feet of the perpendiculars from $C$ onto $OB$ and $OD$ respectively. Prove that $W$, $X$, $Y$, and $Z$ are concyclic.


\item % 


\item % Monthly Assignments 2011
Find all functions $f : \mathbb{N}_0 \to \mathbb{Z}$ such that
\[
  f(a) f(b) f(c) f(d) = f\left(a^2 + b^2 + c^2 + d^2\right)
\]
for all $a, b, c, d \in \mathbb{N}_0$.

\end{enumerate}


\vfill
\begin{itemize}
	\item Submit your solutions at \href{https://forms.gle/T9HNgZgj8EhypBnR6}{https://forms.gle/T9HNgZgj8EhypBnR6}
	\item Submit each question in a single separate PDF file (with multiple pages if necessary).
	\item If you take photographs of your work, use a document scanner such as Office Lens to convert to PDF.
	\item If you have multiple PDF files for a question, combine them using software such as PDFsam.
\end{itemize}

\vfill
% ASCII art
\centering
\small
\begin{BVerbatim}
                         ,.---.   
               ,,,,     /    _ `.
                \\\\   /      \  )
                 |||| /\/``-.__\/
                 ::::/\/_
 {{`-.__.-'(`(^^(^^^(^ 9 `.========='
{{{{{{ { ( ( (  (   (-----:=
 {{.-'~~'-.(,(,,(,,,(__6_.'=========.
                 ::::\/\ 
                 |||| \/\  ,-'/\
                ////   \ `` _/  )
               ''''     \  `   /
                         `---''
\end{BVerbatim}

\end{document}
