\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large Advanced Test 3}
  \\ \vspace{1em}
  \textbf{\large Stellenbosch Camp 2021}
  \\ \vspace{1em}
  \textbf{\large Time: $2\frac{1}{2}$ hours}
\end{center}

\bigskip

\begin{enumerate}[itemsep=\fill]

\item % 
Point $O$ is in the interior of an equilateral triangle $ABC$. Prove that there exists a triangle with edge lengths equal to $OA$, $OB$ and $OC$.

\item % BMO1 2009/10
Aaron attempts all six questions on the SAMO senior paper. For each question, his mark is an integer from 0 to 7. He never scores more points on a later question than on any earlier question. How many different possible sequences of six marks can he achieve? 


\item % 


\item % 105 Algebra Problems, Andreescu
A polynomial $p(x) = x^n +a_1 x^{n-1} +\dotsb +a_{n-1} x +1$ has nonnegative coefficients and all of its roots are real numbers.
Prove that $p(2) \geq 3^n$.


\item % 
Let triangle $ABC$ have circumcircle $\Gamma$. Let $D$ be the intersection of the altitude from $A$ and $\Gamma$, and let $E,F$ be the feet of the altitudes from $B$ and $C$ to $AC$ and $AB$ respectively. Let $H$ be the orthocenter of $ABC$ and $M$ the midpoint of $AH$. A line parallel to $EF$, passing through $M$, intersects $AB$ and $AC$ at $P$ and $Q$ respectively. Prove that $\angle PDF = \angle QDE$.

\end{enumerate}


\vfill
\begin{itemize}
	\item Submit your solutions at \href{https://forms.gle/T9HNgZgj8EhypBnR6}{https://forms.gle/T9HNgZgj8EhypBnR6}
	\item Submit each question in a single separate PDF file (with multiple pages if necessary).
	\item If you take photographs of your work, use a document scanner such as Office Lens to convert to PDF.
	\item If you have multiple PDF files for a question, combine them using software such as PDFsam.
\end{itemize}

\vfill
% ASCII art
\centering
\small
\begin{BVerbatim}
                       7,_   .'.    ,
                   __..'`;`-' | `--;|
                  `\._ `\.`.  `\   |`._./7
                   /_.`>.-~"""`~-. |    ;   _,
             `\..-' .-',/  <_|<| |>-.  | `""/
               |`"7'/'  _.----..<  <|`.;   /:
            __.' /,/ ./'        `\.` ; `. ;  `>
           `\--":/ .'              ` \`\ \  .'
          .__. :;.'     .-"""-.     _..   \/
    ,/'     | / /   ,  :       `. /'.--'   |
  /'/       <; /    |`\ \    _.._:|/   /\  |
 :  :       / /     :  `-'" <     \ ' (_o|/
 :`\.\-._.-' '   j  `\.      `\.__  _  \  |
  \`-.        _.' `.__/          \/'._\,  `\
   /  ,  _.-""                    `\\ 7-. o `>
  :  /,-'                          ,/ `\ `--'
   \ ||                            `-~-" 
    `\_\ 
\end{BVerbatim}

\end{document}
