\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large Advanced Test 2}
  % LEVEL is Senior, Intermediate or Beginner
  % NUMBER is the test number: 1, 2, etc.
  \\ \vspace{1em}
  \textbf{\large Stellenbosch Camp 2021}
  \\ \vspace{1em}
  \textbf{\large Time: $2\frac{1}{2}$ hours}
\end{center}

\bigskip

\begin{enumerate}[itemsep=\fill]

\item % 105 Algebra problems, Andreescu
Prove that
\[ \mspace{-36mu} \frac{1}{(\sqrt{1}+\sqrt{2})(\sqrt[4]{1}+\sqrt[4]{2})} +\frac{1}{(\sqrt{2}+\sqrt{3})(\sqrt[4]{2}+\sqrt[4]{3})} +\dotsb +\frac{1}{(\sqrt{9999}+\sqrt{10000})(\sqrt[4]{9999}+\sqrt[4]{10000})} = 9. \]


\item %
Each of the $19 999$ species of plants in Cape Town are assigned a label from $2$ to $20 000$. Liam's computer stores a list showing each plant species and the label each corresponds to. Dylan's computer stores a list showing each pair of plant species and the greatest common divisor of their labels. The data on Liam's computer was lost after load shedding surged the computer's hard drive. Dylan, however, was responsible and backed up his data. Is it possible to recover Liam's data from Dylan's data?

\item % Portugal 2010
A group of $2021$ students write a test that consists of $2021$ questions. Each question is solved by at least $1011$ students. Prove that there is a group of 10 students such that each question was solved by at least one member of the group.

\item
Let $ABCDE$ be a regular pentagon inscribed in a circle.
Let $X$ be a point on the minor arc $AE$.
Prove that
\begin{flalign*}
  |AX|-|BX|+|CX|-|DX|+|EX| = 0.
\end{flalign*} 


\item % 

\end{enumerate}


\vfill
\begin{itemize}
	\item Submit your solutions at \href{https://forms.gle/T9HNgZgj8EhypBnR6}{https://forms.gle/T9HNgZgj8EhypBnR6}
	\item Submit each question in a single separate PDF file (with multiple pages if necessary).
	\item If you take photographs of your work, use a document scanner such as Office Lens to convert to PDF.
	\item If you have multiple PDF files for a question, combine them using software such as PDFsam.
\end{itemize}

\vfill
% ASCII art
\centering
\begin{BVerbatim}
% Insert art here
\end{BVerbatim}

\end{document}
