\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}
\usepackage{amsfonts}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large Intermediate Test 3}
  \\ \vspace{1em}
  \textbf{\large Stellenbosch Camp 2021}
  \\ \vspace{1em}
  \textbf{\large Time: $2\frac{1}{2}$ hours}
\end{center}

\bigskip

\begin{enumerate}[itemsep=\fill]

\item % 
Sandra and Phil play a game, alternating turns with Sandra moving first. They begin with the numbers 1, 2, 3,...,2021 arranged in a straight line. On their turn, a player may highlight between 1 and 1000 (inclusive) consecutive numbers, as long as none of them have been highlighted before. The player who highlights the last number wins. Who has a winning strategy?


\item % Jean
Find all functions $f: \mathbb{R} \rightarrow \mathbb{R}$ such that:
$$f(xy) + yf(x) + xf(y) = 3xy$$
for all $x, y \in \mathbb{R}$.


\item % 
Find all integer solutions to the equation $$ x^3+y^3=10 000.$$


\item % 
Point $O$ is in the interior of an equilateral triangle $ABC$. Prove that there exists a triangle with edge lengths equal to $OA$, $OB$ and $OC$.


\item % BMO1 2009/10
Aaron attempts all six questions on the SAMO senior paper. For each question, his mark is an integer from 0 to 7. He never scores more points on a later question than on any earlier question. How many different possible sequences of six marks can he achieve? 
\end{enumerate}


\vfill
\begin{itemize}
	\item Submit your solutions at \href{https://forms.gle/T9HNgZgj8EhypBnR6}{https://forms.gle/T9HNgZgj8EhypBnR6}
	\item Submit each question in a single separate PDF file (with multiple pages if necessary).
	\item If you take photographs of your work, use a document scanner such as Office Lens to convert to PDF.
	\item If you have multiple PDF files for a question, combine them using software such as PDFsam.
\end{itemize}

\vfill
% ASCII art
\centering
\small
\begin{BVerbatim}
 O
O
 o  \``/
    /o `))
   /_/\_ss))
       |_ss))/|
      |__ss))_|
     |__sss))_|
     |___ss))\|
      |_ss))
       )_s))
 (`(  /_s))
  (_\/_s))
   (\/))
\end{BVerbatim}

\end{document}
