\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{pgfplots}
\pgfplotsset{compat=1.15}
\usepackage{mathrsfs}
\usetikzlibrary{arrows}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large Intermediate Test 4}
  \\ \vspace{1em}
  \textbf{\large Stellenbosch Camp 2021}
  \\ \vspace{1em}
  \textbf{\large Time: $2\frac{1}{2}$ hours}
\end{center}

\bigskip

\begin{enumerate}[itemsep=\fill]

\item %Cayley 2021
Let $a,b,c,d,e,f \in \mathbb{R}$ satisfy the following two equations: 
$$\frac{d}{a}+\frac{b}{e} = 1 \qquad\text{and}\qquad \frac{e}{b}+\frac{c}{f} = 1.$$
Prove that $abc + def = 0$.


\item %Phil
From points $A$ and $B$ on a circle, equal tangents $AP$ and $BQ$ are drawn, as shown. Prove that $AB$ bisects $PQ$.

\definecolor{xdxdff}{rgb}{0.49019607843137253,0.49019607843137253,1}
\definecolor{uuuuuu}{rgb}{0.2666666666666,0.2666666666666,0.2666666666666}
\begin{center} \begin{tikzpicture}[line cap=round, line join=round, >=triangle 45, x=0.8cm, y=0.8cm]
  \clip(-5,-5) rectangle (6,5);
  \draw [line width=2pt] (0,0) circle (2.8284271247461903);
  \draw [line width=2pt,domain=-9.62:9.62] plot(\x,{(--8-0*\x)/-2.8284271247461903});
  \draw [line width=2pt,domain=-9.62:9.62] plot(\x,{(--8-2.6581372106527787*\x)/-0.9665953493282831});
  \draw [line width=2pt] (4.3668525260863005,3.7323717681139024)-- (5.02,-2.8284271247461903);
  \draw [line width=2pt] (0,-2.8284271247461903)-- (2.6581372106527787,-0.9665953493282831);
  \draw [fill=uuuuuu] (0,-2.8284271247461903) circle (2pt);
  \draw[color=uuuuuu] (0.16,-2.43) node[anchor=south] {A};
  \draw [fill=uuuuuu] (2.6581372106527787,-0.9665953493282831) circle (2pt);
  \draw[color=uuuuuu] (2.82,-0.53) node[anchor=north west] {$B$};
  \draw [fill=uuuuuu] (5.02,-2.8284271247461903) circle (2pt);
  \draw[color=uuuuuu] (5.18,-2.39) node[anchor=south west] {$P$};
  \draw [fill=uuuuuu] (4.3668525260863005,3.7323717681139024) circle (2pt);
  \draw[color=uuuuuu] (4.52,4.13) node[anchor=north west] {$Q$};
\end{tikzpicture} \end{center}


\item% Maclaurin 2019
A \textit{tetromino} is a rectangle with length 4 units and breadth 1 unit. Find all possible natural numbers $n$ such that an $n\times n$ square grid can be exactly tiled by tetronimo tiles.  


\item % Andrew
Let $p$ be an odd prime. Prove that
\[
	\sum_{k=1}^{p-1} (p-k)!k! \equiv \frac{p-1}{2} \pmod{p}.
\]

\vfill
\begin{center}
  \textbf{Please note that there is a second page.}
\end{center}
\clearpage


\item % 
Phil the physicist tries to come up with some equations describing the behaviour of a bucket of salt water as it is diluted by adding pure water. He uses an $m$ kilogram bucket initially containing $s$ kgs of salt and $w$ kgs of water, before $x$ kgs of extra water is added. He uses $k$ as a positive proportionality constant. Phil realises that the following two expressions are important in his study. 
$$\frac{ms+mw}{\frac{kms}{ms+mw}+1} + mx \qquad\text{and}\qquad \frac{ms+mw+mx}{\frac{kms}{ms+mw+mx}+1}.$$
Help Phil by determining which one of these expressions is always bigger than or equal to the other.
\end{enumerate}


\vfill
\begin{itemize}
	\item Submit your solutions at \href{https://forms.gle/T9HNgZgj8EhypBnR6}{https://forms.gle/T9HNgZgj8EhypBnR6}
	\item Submit each question in a single separate PDF file (with multiple pages if necessary).
	\item If you take photographs of your work, use a document scanner such as Office Lens to convert to PDF.
	\item If you have multiple PDF files for a question, combine them using software such as PDFsam.
\end{itemize}

\vfill
% ASCII art
\centering
\small
\begin{BVerbatim}
                        /\
                       /  |
                       \  o
                   _.-`/`-._
       _         _/         \_         _
      ) `-._   _/  /O\   /O\  \_   _.-` (
     )      `-/    `-'   `-'    \-`      (
     )     _.-|      ___        |-._     (
      )_.-`   \   .-'   `-._    /   `-._(
               \   `-.___.--`  /
                "-._       _.-"
                    "-._.-"
\end{BVerbatim}

\end{document}
