\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large Intermediate Test 2}
  \\ \vspace{1em}
  \textbf{\large Stellenbosch Camp 2021}
  \\ \vspace{1em}
  \textbf{\large Time: $2\frac{1}{2}$ hours}
\end{center}

\bigskip

\begin{enumerate}[itemsep=\fill]


\item % Source of problem
A positive integer is written on each face of a cube. Each vertex is the assigned the product of the numbers written on the faces intersecting the vertex. The sum of the numbers assigned to all the vertices is equal to $1001$. Find the sum of the numbers written on the faces of the cube.

\item % Poland 1995
Let $m \in {N}$. How many subsets $S$ are there of $\{2m+1,2m+2,...4m\}$ such that $S$ does not contain $2$ elements which sum to $6m+1$? 

\item % 
Let $ABCD$ be a rectangle and $E$ be a point on the line $DC$ such that $DC = CE$ and $E \neq D$.  Let $M$ be the midpoint of $AB$.  Also let $BC$ intersect $AE$ at $F$, and let $AE$ intersect $CM$ at $P$.  Show that $$\frac{area(APD)}{area(PFD)} = 2$$

\item % 105 Algebra problems, Andreescu
Prove that
\[ \mspace{-36mu} \frac{1}{(\sqrt{1}+\sqrt{2})(\sqrt[4]{1}+\sqrt[4]{2})} +\frac{1}{(\sqrt{2}+\sqrt{3})(\sqrt[4]{2}+\sqrt[4]{3})} +\dotsb +\frac{1}{(\sqrt{9999}+\sqrt{10000})(\sqrt[4]{9999}+\sqrt[4]{10000})} = 9. \]

\item % 
Each of the $19 999$ species of plants in Cape Town are assigned a label from $2$ to $20 000$. Liam's computer stores a list showing each plant species and the label each corresponds to. Dylan's computer stores a list showing each pair of plant species and the greatest common divisor of their labels. The data on Liam's computer was lost after load shedding surged the computer's hard drive. Is it possible to recover Liam's data from Dylan's data?

\end{enumerate}


\vfill
\begin{itemize}
	\item Submit your solutions at \href{https://forms.gle/T9HNgZgj8EhypBnR6}{https://forms.gle/T9HNgZgj8EhypBnR6}
	\item Submit each question in a single separate PDF file (with multiple pages if necessary).
	\item If you take photographs of your work, use a document scanner such as Office Lens to convert to PDF.
	\item If you have multiple PDF files for a question, combine them using software such as PDFsam.
\end{itemize}

\vfill
% ASCII art
\centering
\begin{BVerbatim}
                       _,--._
                      ,'      `.
              |\     / ,-.  ,-. \     /|
              )o),/ ( ( o )( o ) ) \.(o(
             /o/// /|  `-'  `-'  |\ \\\o\
            / / |\ \(   .    ,   )/ /| \ \
            | | \o`-/    `\/'    \-'o/ | |
            \ \  `,'              `.'  / /
         \.  \ `-'  ,'|   /\   |`.  `-' /  ,/
          \`. `.__,' /   /  \   \ `.__,' ,'/
           \o\     ,'  ,'    `.  `.     /o/
            \o`---'  ,'        `.  `---'o/
             `.____,'            `.____,
\end{BVerbatim}

\end{document}
