\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large Intermediate Test 1 Solutions}
  % LEVEL is Senior, Intermediate or Beginner
  % NUMBER is the test number: 1, 2, etc.
  \\ \vspace{1em}
  \textbf{\large Stellenbosch Camp 2021}
  \\ \vspace{1em}
\end{center}

\vspace{24pt}

\begin{enumerate}[1.]

\item % AMC 10A 2014
In rectangle $ABCD$, $|\overline{AB}|=1$, $|\overline{BC}|=2$, and points $E$, $F$, and $G$ are midpoints of $\overline{BC}$, $\overline{CD}$, and $\overline{AD}$, respectively.
Point $H$ is the midpoint of $\overline{GE}$.
Lines $AF$ and $DH$ intersect at point $X$, and lines $BF$ and $CH$ intersect at point $Y$.
What is the area of rectangle $XHYF$?

\textbf{Solution:} 

\item % Phil
A permutable prime is a prime number which remains prime when its digits are rearranged in all possible ways. Show that a permutable prime cannot be a four digit number where all the digits are distinct.

\textbf{Solution:} Note that no four-digit permutable prime can contain any of the digits $0,2,4,5,6,8$ since any number ending in these digits is divisible by $2$ or $5$ and hence is not prime. Hence the four distinct digits must be $1,3,7,9$. However, this is impossible since the number $1379 = 7 \times 197$ is not prime. 

\item % Phil
Show that, for all real numbers $a$, $b$, and $c$,
\[ 2021 \geq 4a + 18b + 88c - a^2 - b^2 - c^2. \]

\textbf{Solution:} We complete the square to obtain:  \begin{align*}
 2021-4-81-1936 &\geq (-a^2+4a- 4) + (-b^2+18b-81) + (-c^2+88c-1936) \\
							\iff	0 &\geq -(a-2)^2 -(b-9)^2 -(c-44)^2\\
							\iff	(a-2)^2 + (b-9)^2 + (c-44)^2 &\geq 0
\end{align*} 
This follows from the fact that all squares are nonnegative.


\item % Ireland 2014
How many ways are there to choose $24$ black squares from a standard chess board (with $32$ black and $32$ white squares alternating) such that exactly three squares are chosen in each row and in each column?

\textbf{Solution:} Since each row and each solumn has 4 black squares, the question is equivalent to choosing 8 black squares such that each row and each column has one chosen square. Considering rows 1,3,5 and 7, we see there there are 4 options to choose the square in row 1, then 3 options in row 3, 2 options in row 5, and 1 in row 7, for a total of $4! = 24$ options. Similarly, there are 24 options to choose the squares in rows 2,4,6 and 8. This gives a total of $24\times24 = 576$ possibilities.

\item % 

\textbf{Solution:}

\end{enumerate}

\end{document}