\documentclass{article}
\usepackage{mathtools,amsfonts}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}


\begin{document}
	\thispagestyle{empty}
	
	\begin{center}
		\textbf{\Large Intermediate Assignment 3}
		\\ \vspace{1em}
		\textbf{\large Due: }
	\end{center}
	
	\bigskip
	\begin{enumerate}[itemsep=12pt]
		
		\item %Nederlande Wiskunde Olympiade R2 2018
		You have balls that are numbered from $1$ to $n$. You need to distribute 
		the balls into two boxes. The \textit{value} of a box is the sum of the numbers in that that. Your distribution of balls must satisfy the following rules: \\ 
		\begin{enumerate}
			\item Each box has at least one ball.
			\item The two boxes do not have the same number of balls.
			\item The value of the box with the least number of balls must be at least $2$ more than the  value of the box with the most balls. 
		\end{enumerate}
	Determine for which positive integers $n$ this is possible. 
		
		
		\item %Island Hopping Holidays Q14
		In triangle $ABC$ sides $AB$ and $BC$ are extended to $K$ and $L$, respectively, such that $B$ is the midpoint of $AK$ and $C$ is the midpoint of $BL$. The intersection of $AC$ and $KL$ is at $P$.
		\\ Prove that $|AC| = 3|CP|$.
		
		
		\item Determine all triples $(x,y,z)$ of \textit{distinct} real numbers that satisfy the following system of equations:
		\begin{itemize}
			\item $x^2+y^2 = -x+3y+z$
			\item $y^2+z^2 = x+3y-z$
			\item $x^2+z^2 = 2x+2y-z$
		\end{itemize}
		
		\item %Czech and Slovak MO 2017
		Find all primes $p$ for which there exists a positive integer $n$ such that $p^n+1$ is a cube of a positive integer.
		
		
		\item %Czech and Slovak MO 2016
		Find the smallest positive integer that can be inserted between numbers $20$ and $16$ so that the resulting number $20 \dots 16$ is a multiple of $2016$.
		
		
		\item % DB-2016-2
		For which real numbers $s$ and $t$ does the polynomial $p(x) = X^3 -(2s+t)X^2 +(2s^2+t^2)X +3st$ have three (not necessarily distinct) real roots? 
		
	\end{enumerate}
	
	
	\vfill
	\small
	\begin{itemize}
		\item Submit your solutions at \href{https://forms.gle/Pv89v957obJMEAw26}{https://forms.gle/Pv89v957obJMEAw26}
		\item Submit each question in a single separate PDF file (with multiple pages if necessary).
		\item If you take photographs of your work, use a document scanner such as Office Lens to convert to PDF.
		\item If you have multiple PDF files for a question, combine them using software such as PDFsam.
	\end{itemize}
	
	\vfill
	% ASCII art
	\centering
	\small
	\begin{BVerbatim}
		_________         .    .
		(..       \_    ,  |\  /|
		\       O  \  /|  \ \/ /
		\______    \/ |   \  / 
		vvvv\    \ |   /  |
		\^^^^  ==   \_/   |
		`\_   ===    \.  |
		/ /\_   \ /      |
		|/   \_  \|      /
		\________/
	\end{BVerbatim}
	
\end{document}
