\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large Intermediate February Problem Set}
  \\ \vspace{1em}
  \textbf{\large Due: <DATE>}
\end{center}

\bigskip

\begin{enumerate}[itemsep=\fill]


\item % 


\item % 


\item % Kazakstan 2008
Find all real numbers $x_1$, $x_2$, \ldots, $x_{2021}$ such that
\[ (2022-x_1)^2 +(x_1-x_2)^2 +(x_2-x_3)^2 +\dotsb +(x_{2020}-x_{2021})^2 +x_{2021}^2 = 2022. \]~


\item %Turkey Junior 1999
Let $\Gamma$ be a circle with centre $O$ and radius $1$.
Let $A$, $B$, $C$, and $D$ be points on $\Gamma$ such that $AB \parallel CD$ and $AB$ is a diameter of $\Gamma$.
Let $l$ be the line through $A$ tangent to $\Gamma$ and let $BC$ and $BD$ intersect $l$ at $X$ and $Y$ respectively.
Find $|AX| \cdot |AY|$.


\item %Finland 2009
For which $z \in \mathbb{Z}$ does there exist a polynomial $P$ with integer coefficients such that $P(2021) = 2022$ and $P(z) = z$?


\item % Centroamerican 2018
Liam and Dylan play a game, alternating turns with Liam playing first.
At the start, there is a pile of $1 +2 +\dotsb +2022$ stones.
On his turn, a player chooses a positive integer $n$ between $1$ and $2022$ inclusive such that neither player has previously chosen this $n$.
He then removes $n$ stones from the pile and keeps them next to him.
Once the pile is empty, the winner is the player with an even number of stones next to him.
Who has the winning strategy? 

\end{enumerate}


\vfill
\small
\begin{itemize}
	\item Submit your solutions at \href{https://forms.gle/Pv89v957obJMEAw26}{https://forms.gle/Pv89v957obJMEAw26}
	\item Submit each question in a single separate PDF file (with multiple pages if necessary).
	\item If you take photographs of your work, use a document scanner such as Office Lens to convert to PDF.
	\item If you have multiple PDF files for a question, combine them using software such as PDFsam.
\end{itemize}

\vfill
% ASCII art
\centering
\small
\begin{BVerbatim}
% Insert art here
\end{BVerbatim}

\end{document}